Import Jaz data

### 2023-12-04 Code/JazDataImport.Rmd
Fixed file path assignments.

#DataIn <- file.path("..", "Jaz", fsep = .Platform$file.sep)
DataIn <- file.path("..", "MultiCultiSpectra", fsep = .Platform$file.sep)

#ExpDate <- "20220520"
DataOut<- file.path("..", "ImportedData", "Jaz", fsep = .Platform$file.sep)
#CatalogGoogle <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"

@@

```{r read Jaz data using map_df}
fread_plus <- function(Flnm, Skip, FileEncode, Delim){data.table::fread(file = Flnm, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE) %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
}

@@

# JazSpec |>
#   ggplot() +
#   geom_point(aes(x = Wavelength, y = Counts)) +
#   theme_bw()
```

@@

```{r remove the wl < 350 and > 750}

@@

```
ggspectra:
https://cran.r-project.org/web/packages/ggspectra/vignettes/userguide1-grammar.html
https://cran.r-project.org/web/packages/ggspectra/vignettes/userguide2-autoplot-methods.html
```{r}

@@

```{r save rds}
 saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "MultiCultiSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))
```

>>>>

DataIn <- file.path("..", "Data","RawData", "MCEmissionSpectra", fsep = .Platform$file.sep)

DataOut<- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)

@@

```{r read Jaz data using map_df}

fread_plus <- function(Flnm, Skip, FileEncode, Delim){data.table::fread(file = Flnm, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE) %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
}

@@

# JazSpec |>
#   ggplot() +
#   geom_point(aes(x = Wavelength, y = Counts)) +
#   theme_bw()

@@

```{r remove wl < 350 and > 750}

@@

ggspectra:
https://cran.r-project.org/web/packages/ggspectra/vignettes/userguide1-grammar.html
https://cran.r-project.org/web/packages/ggspectra/vignettes/userguide2-autoplot-methods.html
```{r}

@@

```{r save rds}

 saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "MultiCultiSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))
